### 2021-09-20 documentos/pce.tex
pequeñez
They came from... Behind

@@

It can be seen from Kraus decomposition that quantum channels preserve hermiticity, this has a practical consequence when using hermitian bases. $\hat \mcE_{ij}=1/2^N\tr\left( \sigma_i \mcE[\sigma_j]
 \right)$

@@

>>>>

Quantum channels have the well-known \textit{Kraus representation} (or operator-sum representation) which reads $\mcE[\rho]=\sum_i K_i \rho K^\dagger{}_i$ in fact, a linear operation is completely positive if and only if it has a Kraus representation [cite Kraus book]

@@

It can be seen from Kraus decomposition that quantum channels preserve hermiticity, this has a practical consequence when using hermitian bases. $\hat \mcE_{ij}=\tr\left( \Delta_i \mcE[\Delta_j]
 \right)$

@@

A graphical representation for 1, 2 and 3 qubits may be introduced, being the
two qubit case what has proved more useful. Consider a $N$ dimensional 
grid, with $4^N$ places. Each place has $N$ integer coordinates, ranging
from 0 to 3, so each place corresponds to a given $\vec \alpha$ in 
\eref{eq:N_qubits_rho}. For a given PCE, we shall fill with black 
the corresponding position \cpnote{No me pone feliz esta redaccion}
if the corresponding $\tau_{\vec \alpha}=1$. Otherwise, we leave it 
empty. Examples for $N=1$ are provided in \fref{fig:one:qubit:examples}, whereas
for two qubits, we exemplify them in \fref{fig:two:qubit:examples}. Notice
than in both cases we drop the label $\alpha$ for simplicity, as it will 
remain unchanged throughout this text.

\begin{figure} % {{{
\begin{center}
\begin{tikzpicture}[x=0.5cm, y=0.5cm]
% Coordenadas  
\node at (-0.6,0.5) {(a)} ;
\draw (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_0$} ;
\begin{scope}[shift={(0,-1)}]
\draw (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_1$} ;
\end{scope}
\begin{scope}[shift={(0,-2)}]
\draw (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_2$} ;
\end{scope}
\begin{scope}[shift={(0,-3)}]
\draw (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_3$} ;
\end{scope}
% Identity
\begin{scope}[shift={(4,0)}]
\node at (-0.6,0.5) {(b)} ;
\fill[black] (0,0) rectangle (1,1);
\draw (0,0) rectangle (1,1);
\begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
\end{scope}
% Dephasing
\begin{scope}[shift={(8,0)}]
\node at (-0.6,0.5) {(c)} ;
\fill[black] (0,0) rectangle (1,1);
\draw (0,0) rectangle (1,1);
% \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
\end{scope}
% Total depolarization
\begin{scope}[shift={(12,0)}]
\node at (-0.6,0.5) {(d)} ;
\fill[black] (0,0) rectangle (1,1);
\draw (0,0) rectangle (1,1);
% \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
\end{scope}
\end{tikzpicture}
\end{center}
	\caption{\cpnote{Aca meter la figura, JA} In (a) we introduce the positions of the single 
qubit diagrams, so that each square corresponds to a single 
$\tau_{\alpha}$, $\alpha=0,\cdots,3$. The diagrams in 
(b), (c) and (d) correspond to the identity map, \cpnote{bit flip ao algo asi}, and 
total depolarization, respectively. In (e) we show a map that erases the two components
$r_1$ and $r_2$ and thus does not correspond to a quantum operation.}
	\label{fig:one:qubit:examples}
\end{figure} % }}}

\begin{figure} % {{{
	\caption{\cpnote{Aca meter la figura, JA} In (a) we introduce the
positions of two qubit diagrams. The diagrams in 
(b) corresponds to a quantum channel that \cpnote{ver con JA que ejemplo ponemos}, 
and in (c) a diagram of a map that is not a quantum channel is presented.}
	\label{fig:two:qubit:examples}
\end{figure} % }}}
